Conference Paper Title\\

### 2023-06-13 LARS_paper/paper.tex
Restructure abstract and joint state controller paragraph

\begin{abstract}
  With the growth of robotics, mobile robots are increasingly becoming a common aspect in key sectors of the economy. When compared to wheeled and tracked robots, legged robots present greater mobility and maneuverability, but less locomotion stability, which in turn demands more complex control systems. This paper aims to develop a quadruped robot capable of walking when teleoperated and assess its locomotion performance based on experiments. The first part of the methodology was dedicated to research and the definition of the robot's concept. The following stage involved the development of the robot's software, simulation, and, in parallel, the design, fabrication and assembly of the prototype. After both stages were done, the software was integrated into the prototype. After the integration stage, the locomotion experiments were conducted. Based on these experiments, it was possible to conclude that the robot was able to perform gaits of different sizes and walk in both plane and uneven terrains. Furthermore, it was observed that the body's rotation PID controller contributed to reducing the oscillation of the robot's body in both roll and pitch during walking in both terrains.
\end{abstract}

@@

This paper is divided as follows: section X presents the development of the robot, focusing on the gait planner, the kinematic model, the stabilization control and the trajectory planner implementations. In section X, the experiments conducted to evaluate and validate the effectiveness of the designed controller through statistical analysis are explained. Finally, section X presents the conclusions and suggestions for future work.

\section{Robot Development}

INTRO

@@

A small quadruped was designed and developed for research (Fig. X).
During the prototyping phase, the hardware architecture and physics structure was designed. Following that, the structure of the robot was printed and integrated with the hardware components. The robot's actuators are servo motors of the model dynamixel MX-28, and a Raspberry Pi 4 was chosen as the processing unit. Furthermore, it contains an inertial sensor, model MPU6050. All the software was developed with the Robot Operating System 2 Humble (ROS 2) \cite{ROS2Humble}.

IMAGEM DO ROBO

The robot's structure is mammal-type, which is characterized by the presence of two joints in the sagittal plane, similar to animals such as dogs and horses.  The robot's legs follow a configuration called full-elbow, in which the four legs are oriented backward, as shown in Fig. X. Furthermore, it features 3 degrees of freedom (DoF) per leg, providing the legs with substantial freedom of movement. The robot was designed to favor the mass balance between the body and the robot's legs, that is, the majority of its mass is located in the body or as close to it as possible. Lighter legs can move quickly without significantly changing the center of gravity of the robot, which increases stability and requires less control complexity.  On the other hand, the legs should be strong enough to support the robot's weight and the impact on the ground.

@@

<REESTRUTURAR ESSE PARAGRAFO>

The gait planner is responsible for controlling each leg and the robot's body. It defines where each foot will step and where the body should move based on the desired velocity command. Through a trajectory planner, it calculates the trajectory each foot and body should follow based on the velocity command. The gait planner then reads the pitch and roll angles of the body from the stabilization controller

The gait planner then sends commands to each joint based on the planned trajectories and the control efforts from the stabilization controller of the body at a frequency of $\SI{50}{\hertz}$. To convert both trajectories' points and the control efforts into the angles of the joints, a kinematic model is used, which is responsible for mapping the three-dimensional position of one foot to the joints' angles of its respective leg.

@@

\begin{figure*}[h]
  \centering
  \begin{subfigure}[t]{0.32\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{Cycloid_space.png}
    \caption{Curva no espaço 3D.}
    \label{fig:traj_space}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{Cycloid_time.png}
    \caption{Curva no tempo.}
    \label{fig:traj_time}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{Cycloid_modified.png}
    \caption{Curva com disposição de pontos modificada.}
    \label{fig:traj_time_modified}
  \end{subfigure}
  \vfill
  \caption{Trajetórias cicloidais para o passo de robô.}
  Fonte: autores.
  \label{fig:traj_curve}
\end{figure*}

@@

The control subsystem of the robot is composed of two main components: the joints' controllers, and the body's stabilization controller. The joints' controllers, each one a PID, are responsible for controlling each joint of the robot independently. Meanwhile, the body's stabilization controller is responsible for controlling the pitch and roll angles of the robot, maintaining it at 0 degrees.

<APROFUNDAR JOINT CONTROLLER>

@@

\section{Results}

@@

\begin{figure}[!htb]
  \centering
  \begin{subfigure}[t]{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{plane_boxplot.png}
    \caption{Terreno plano.}
    \label{fig:imu_test_plane}
  \end{subfigure}
  \begin{subfigure}[t]{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{irregular_boxplot.png}
    \caption{Terreno irregular.}
    \label{fig:imu_test_irregular}
  \end{subfigure}
  \caption{Oscilação do corpo em ambos os tipos de terreno.}
  Fonte: autores.
  \label{fig:imu_test}
\end{figure}

\section{Conclusion}

>>>>

\begin{abstract}
  With the growth of robotics, mobile robots are increasingly becoming common in key sectors of the economy. When compared to wheeled and tracked robots, legged robots present greater mobility and maneuverability, but less locomotion stability, which in turn demands more complex control systems. This paper aims to develop a quadruped robot and a PID  stabilization controller to compensate for the body oscillation during the walk. This work presents the development of the mobile robot platform, including the prototype, the gait planner, the kinematic model, and the control subsystem. Finally, locomotion experiments were conducted to assess the robot's locomotion performance when using the stabilization controller. The experiments were realized in terrains flat and uneven. Therefore, it was observed that the stabilization controller contributed to reducing the oscillation of the robot's body in both roll and pitch during walking in both terrains.
\end{abstract}

@@

This paper is divided as follows: section \ref{development} presents the development of the robot, focusing on the gait planner, the kinematic model, the stabilization control and the trajectory planner implementations. In section \ref{results}, the experiments conducted to evaluate and validate the effectiveness of the designed controller through statistical analysis are explained. Finally, section \ref{conclusion} presents the conclusions and suggestions for future work.

\section{Robot Development} \label{development}

The robot platform designed and developed for this research is presented in the Fig. \ref{fig:robot}.

\begin{figure}[!htb]
  \centering
  \caption{The quadruped robot developed for this research}
  \includegraphics[width=0.25\textwidth]{robot.jpeg}
  \vfill
  % \vspace{-\baselineskip}
  \label{fig:robot}
\end{figure}

@@

During the prototyping phase, the hardware architecture and physics structure was designed. Following that, the structure of the robot was printed and integrated with the hardware components. The robot's actuators are servo motors of the model dynamixel MX-28, and a Raspberry Pi 4 was chosen as the processing unit. Furthermore, it contains an inertial sensor, model MPU6050. All the software was developed with the Robot Operating System 2 Humble (ROS 2) \cite{ROS2Humble}.

The robot's structure is mammal-type, which is characterized by the presence of two joints in the sagittal plane, similar to animals such as dogs and horses.  The robot's legs follow a configuration called full-elbow, in which the four legs are oriented backward, as shown in \ref{fig:robot}. Furthermore, it features 3 degrees of freedom (DoF) per leg, providing the legs with substantial freedom of movement. The robot was designed to favor the mass balance between the body and the robot's legs, that is, the majority of its mass is located in the body or as close to it as possible. Lighter legs can move quickly without significantly changing the center of gravity of the robot, which increases stability and requires less control complexity.  On the other hand, the legs should be strong enough to support the robot's weight and the impact on the ground.

@@

For the robot to move according to the adopted gait pattern, there is a gait planner responsible for commanding the robot's legs. The gait planner defines where each foot will step and where the body should move based on the velocity command. Through a trajectory planner, it calculates the trajectory each foot and body should follow. Then, the gait planner reads, from the stabilization controller, the corrections in pitch and roll angles and applies them before sending the commands to each joint, at a frequency of $\SI{50}{\hertz}$. To convert both trajectories' points and the control efforts into the angles of the joints, a kinematic model is used, which is responsible for mapping the three-dimensional position of one foot to the joints' angles of its respective leg.

@@

\begin{figure*}[h]
  \centering
  \begin{subfigure}[t]{0.32\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{Cycloid_space.png}
    \caption{The cycloidal curve in 3D space.}
    \label{fig:traj_space}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{Cycloid_time.png}
    \caption{The cycloidal curve in the time.}
    \label{fig:traj_time}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{Cycloid_modified.png}
    \caption{The curve with the distribution of points modified.}
    \label{fig:traj_time_modified}
  \end{subfigure}
  \vfill
  \caption{Cycloidal trajectories by the trajectory planner.}
  Fonte: autores.
  \label{fig:traj_curve}
\end{figure*}

@@

The control subsystem of the robot is composed of two main components: the joints' controllers, and the body's stabilization controller. The joints' controllers are responsible for controlling each joint of the robot independently. Meanwhile, the body's stabilization controller is responsible for controlling the pitch and roll angles of the robot, maintaining it at 0 degrees.

The joints' controllers is the Joint Trajectory Controller, a controller of ROS which executes joint-space trajectories on a group of joints. According to REF, trajectories are specified as a set of waypoints to be reached at specific time instants, which the controller attempts to execute as well as the mechanism allows. In this work, the waypoints consist of positions and are reached using PID controllers loop-closed.

@@

\section{Results} \label{results}

@@

\begin{figure}[!htb]
  \centering
  \begin{subfigure}[t]{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{plane_boxplot.png}
    \caption{Flat terrain.}
    \label{fig:imu_test_plane}
  \end{subfigure}
  \begin{subfigure}[t]{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{irregular_boxplot.png}
    \caption{Uneven terrain.}
    \label{fig:imu_test_irregular}
  \end{subfigure}
  \caption{Robot body's oscillation in both terrains
  Oscilação do corpo em ambos os tipos de terreno.}
  Fonte: autores.
  \label{fig:imu_test}
\end{figure}

\section{Conclusion} \label{conclusion}
